Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-03-17 answer-to-reviewers.tex

\begin{frontmatter}
\title{Answer to Reviewers' Comments on our Manuscript
``Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability''}

\author[tue]{Gero Walter}
\ead{g.m.walter@tue.nl}
\author[tue]{Simme Douwe Flapper}
\ead{s.d.p.flapper@tue.nl}

\address[tue]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, Netherlands}

\begin{abstract}
We would like to thank the three anonymous reviewers for their detailed and constructive comments,
and their overall positive votum***.
We reproduce their comments here verbatim,
and have numbered the reviewers' comments and questions to allow for easy referencing. 
Our answers are interlaced and typeset in \emph{italic}.
\end{abstract}
\end{frontmatter}

@@

\subsection*{Technical comments}

\begin{enumerate}
\item The notational choice does not seem to be the most appropriate. The use of $\tnow$ is confusing and makes the reading of the paper cumbersome. I will suggest to use something more direct, as $t_j$, where $j=1,\ldots$ represents the $j$th scheduled intervention. With that choice, the notation $\tau^{\tnow}_*$ can be simplified to $\tau^*_j$ without any loss of generality of information. Moreover, with this notational choice (or a similar one) the expression $t_j=j \delta$ becomes natural and. [sic!]

\smallskip

\emph{***This conflicts with our approach that evaluates the RLD and $\tausnow$ also at the exact times of component failures!***\\
maybe something like
$\big\{ t_j: (t_j = m\delta, m \in \naturals_0) \cup (t_j = t_{k,i}, k \in \{1,\ldots,K\}, i \in \{1,\ldots, N_k\}) \big\}$ ???
But this is also quite complex!***}

@@

\emph{p.~3: ``where an operational cycle starts with a new system,
and ends after this system has been replaced by an as good as new system''\\
Section~5: ``An operational cycle begins with system start-up,
and ends when either preventive maintenance is carried out, or a failure of the system occurs,
with subsequent corrective maintenance.''\\
*** I don't quite see the conflict, maybe mention in Sec~5 directly after that sentence that maintenance means replacing the whole system?
And write on p.~3 ``begins with the start-up of a new system'', or even
``An operational cycle spans the time between two consecutive system maintenance actions / replacements.
We thus optimize the unit cost rate calculated over the time since the last system replacement.''
?***}

\item I suggest the authors to define all the acronyms on their first use. For example, CBM is used throughout the text, but never defined; and RDL is used from page 2, but not defined until page 3 (in Section 2).

\smallskip

\emph{CBM was defined in the first line of Section~1, where we wrote ``CBM (condition-based maintenance)''.
We now write ``condition-based maintenance (CBM)'' instead.
We are sorry that we indeed defined RLD too late, and now define it at the first use on page~2.***}

@@

\smallskip

\emph{*** yes, we should mention this in the introduction.}

\item Some variables are not properly defined, e.g. $\Rsys$ or $\Tsys$. The meaning of $C^k_l$ can be guessed from the context, but for completeness should be clearly stated.

\emph{***We define $\Rsys(t) = P(\Tsys > t)$ on p.~5 above Equation~1,
but indeed did not introduce $\Tsys$ as the random failure time of the system.
We do so now in *** (start of Section~3?)}

@@

\emph{***We define $\Rsys(t) = P(\Tsys > t)$ on p.~5 above Equation~1,
but indeed did not introduce $\Tsys$ as the random failure time of the system.
We do so now in *** (start of Section~3?)}

\item As it seems, some of the results in section 4 have been developed elsewhere by one of the authors of this paper. Given that Section 4.1 does not add to the understanding of the problem under discussion, I will suggest to omit it or to include it as an appendix to the manuscript. This is only an opinion and I will understand if the authors decide to ignore my comment.

\emph{*** Section~4.1 introduces the Weibull component models
and the conjugate inverse Gamma prior distribution in our non-standard parametrization,
explaining the Bayesian parameter update step for right-censored lifetimes.
We think that Section~4.1 is crucial to the understanding of our method,
especially for readers not familiar with Bayesian approaches.
As mentioned in our answer to Reviewer~1's main comment,
Sections~4.1 to 4.3 combine results from several parts of the cited manuscript
in a from that is adapted to the purpose of the present manuscript.
We thus think that it is preferable to keep Section~4.1 within the main part of the manuscript.}

@@

\emph{*** Section~4.1 introduces the Weibull component models
and the conjugate inverse Gamma prior distribution in our non-standard parametrization,
explaining the Bayesian parameter update step for right-censored lifetimes.
We think that Section~4.1 is crucial to the understanding of our method,
especially for readers not familiar with Bayesian approaches.
As mentioned in our answer to Reviewer~1's main comment,
Sections~4.1 to 4.3 combine results from several parts of the cited manuscript
in a from that is adapted to the purpose of the present manuscript.
We thus think that it is preferable to keep Section~4.1 within the main part of the manuscript.}

\item I suggest to place Figure 2 somewhere after parameters $m$ and $\delta$ are defined and the maintenance policy is described in Section 5.1 (for example at the end of the section). Otherwise, it is hard to follow.

\emph{We had placed Figure~2 (depicting the flowchat for the policy) directly before Section~5.1 which explains the policy,
and agree that it should appear during or after Section~5.1 to avoid confusion.***}

@@

\emph{We had placed Figure~2 (depicting the flowchat for the policy) directly before Section~5.1 which explains the policy,
and agree that it should appear during or after Section~5.1 to avoid confusion.***}

\item A timeline sketch depicting the evolution of the policy on time, where the different elements of a time grid are illustrated, will be welcome.

\emph{We agree with Reviewer~2 that such a sketch is helpful, and provide it now as Figure~***.}

@@

\emph{We agree with Reviewer~2 that such a sketch is helpful, and provide it now as Figure~***.}

\item Even though the use of the zero sub-indexed double struck capital N is correct for positive naturals and zero, I think that the simpler double struck capital N is enough. The context makes evident the inclusion of zero.

\emph{??? Reviewer~2 suggests to use $\naturals$ in place of $\naturals_0$.
***I don't think this is a good idea, with $\naturals_0$ we emphasize that
we evaluate the RLD for the first time directly at system startup time 0.***}

@@

\smallskip

\emph{Thanks for pointing this out, done.}

\item Frequent references to function $g$, which is only defined later in Section 5.2, make the lecture of the manuscript difficult. I suggest to rewrite the section seeking for all elements to be introduced in a more orderly fashion.

\emph{***We rewrote the entire section as requested, and hope that this is now more clear.
Our intention was to establish the cost rate function $g^{(\tnow)}(\cdot)$ as a generic function first
and to explain the details of its calculation later***}

\item As Section 8 concludes the manuscript, I will suggest to refer to it as “the conclusion” rather than Section 8; e.g. at the end of sections 5.1 and 5.2.

\emph{***Agreed, we now write ``the conclusion (Section~8)''.}
\end{enumerate}

### 2017-03-17 cbm-rbd-paper.tex
Reviewer 2 general comments completed, including small changes in manuscript

Define a grid of planned evaluation time points as $\{m \delta : m \in \naturals_0\}$,
%where $m = 0, 1, 2, \ldots$,
%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
with $\delta$ a sufficiently small time increment.
During an operational cycle,
$\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
However, if a component fails before the next $\tnow$ on the grid,
$\tnow$ is set instead to the exact failure time $t_{k,i}$.
Next, we check whether the system has failed due to this component failure.
If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
If the system has not failed, we calculate $\tausnow$ is for the current off-grid time $\tnow = t_{k,i}$,
and move back onto the grid afterwards,
unless there is another component failure before the next planned evaluation time.

@@

We assume that both preventive and corrective maintenance result in an (as good as) new system state by replacing all components,
such that the system begins a new operational cycle always under the same conditions.
Replacement schemes that do not replace all components would require to account for the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper,
since optimizing over replacement schemes is, in our view, a higly interesting topic
that merits an investigation of its own,
and we will comment on this in Section~\ref{sec:outlook}.
%
%As we use a one-cycle criterion, the time both preventive and corrective maintenance actions require
%does not matter directly for the determination of $\tausnow$.
%Longer downtime and other negative effects of corrective maintenance
%are instead accounted for through the costs parameters $c_p$ and $c_c$ used in the trade-off leading to $\tausnow$,
%as described next.

@@

$\tausnow := \arg\min \gnow(\tau)$
is the cost-optimal time to maintenance as of $\tnow$,
incorporating all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
%illustrates the derivation of $\tausnow$ .
%Minimizing $\gnow(\tau)$ leads to $\tausnow$,
%the optimal moment of maintenance on a prospective time scale.
The minimal expected operational cycle cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
thus is, as of $\tnow$, the lowest cost rate for the current operational cycle
that we can expected to attain.
%attainable for the span of the remaining lifetime of the system,
%i.e., for what happens beyond current time $\tnow$.
%$\gstarnow$ increases over time since 
%***Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
%This gives the expected unit cost rate calculated over the full time since system start-up,
%under the assumption that maintenance is scheduled for $\tstarnow := \tnow + \tausnow$.
$\gstarnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time period.
However, when many (or few but critical) components fail, $\gstarnow$ may increase,
since then, system failure becomes much more likely, leading to a higher risk of incurring the corrective maintenance cost $c_c$.
Figure~\ref{fig:tauhist1fig2T} illustrates these relations for the scenario depicted in Figure~\ref{fig:ghist1fig2T}.
%
As can be seen there and in the numerical examples in Section~\ref{sec:examples},
for continuous component lifetime distributions,
$\tausnow$ is a smooth function of $\tnow$ during periods where no component fails,
with discrete jumps at component failure times.
The size of the jump depends on the relevance of the failed component for the current system reliability.
Common cause failures, i.e., failures of several components at the same time due to a shared root cause,
are currently not accounted for in our model. %, as we assume component failures to be mutually independent
%given the component model parameters.
Such simulatenous failures will seriously influence the RLD and thus $\tausnow$.
We will return to this in Section~\ref{sec:outlook}.
%
%Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
%for our choice of component model.

>>>>

Define a grid of planned evaluation time points as $\{m \delta : m \in \naturals_0\}$,
%where $m = 0, 1, 2, \ldots$,
%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
with $\delta$ a sufficiently small time increment.
During an operational cycle,
$\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
However, if a component fails before the next $\tnow$ on the grid,
$\tnow$ is set instead to the exact failure time $t_{k,i}$.
Next, we check whether the system has failed due to this component failure.
If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
If the system has not failed, we calculate $\tausnow$ for the current off-grid time $\tnow = t_{k,i}$,
and move back onto the grid afterwards,
unless there is another component failure before the next planned evaluation time.

@@

We assume that both preventive and corrective maintenance result in an (as good as) new system state by replacing all components,
such that the system begins a new operational cycle always under the same conditions.
Replacement schemes that do not replace all components would require to account for the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper,
since optimizing over replacement schemes is, in our view, a higly interesting topic
that merits an investigation of its own,
and we will comment on this in the conclusion (Section~\ref{sec:outlook}).
%
%As we use a one-cycle criterion, the time both preventive and corrective maintenance actions require
%does not matter directly for the determination of $\tausnow$.
%Longer downtime and other negative effects of corrective maintenance
%are instead accounted for through the costs parameters $c_p$ and $c_c$ used in the trade-off leading to $\tausnow$,
%as described next.

@@

$\tausnow := \arg\min \gnow(\tau)$
is the cost-optimal time to maintenance as of $\tnow$,
incorporating all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
%illustrates the derivation of $\tausnow$ .
%Minimizing $\gnow(\tau)$ leads to $\tausnow$,
%the optimal moment of maintenance on a prospective time scale.
The minimal expected operational cycle cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
thus is, as of $\tnow$, the lowest cost rate for the current operational cycle
that we can expected to attain.
%attainable for the span of the remaining lifetime of the system,
%i.e., for what happens beyond current time $\tnow$.
%$\gstarnow$ increases over time since 
%***Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
%This gives the expected unit cost rate calculated over the full time since system start-up,
%under the assumption that maintenance is scheduled for $\tstarnow := \tnow + \tausnow$.
$\gstarnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time period.
However, when many (or few but critical) components fail, $\gstarnow$ may increase,
since then, system failure becomes much more likely, leading to a higher risk of incurring the corrective maintenance cost $c_c$.
Figure~\ref{fig:tauhist1fig2T} illustrates these relations for the scenario depicted in Figure~\ref{fig:ghist1fig2T}.
%
As can be seen there and in the numerical examples in Section~\ref{sec:examples},
for continuous component lifetime distributions,
$\tausnow$ is a smooth function of $\tnow$ during periods where no component fails,
with discrete jumps at component failure times.
The size of the jump depends on the relevance of the failed component for the current system reliability.
Common cause failures, i.e., failures of several components at the same time due to a shared root cause,
are currently not accounted for in our model. %, as we assume component failures to be mutually independent
%given the component model parameters.
Such simulatenous failures will seriously influence the RLD and thus $\tausnow$.
We will return to this in the conclusion (Section~\ref{sec:outlook}).
%
%Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
%for our choice of component model.
